Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Edits to definitions

\begin{defn}
  ``The efficacy of the installation, uninstallation or reinstallation process
  of a software product in a specified environment'' (\citep{iso201017043})
\end{defn}

@@

Definition~\ref{DefnInstallability}.

@@

\begin{defn} \label{CorrectDefnSelected} 
  A software is correct if it functions according to its specified functional
  and non-functional specification \citep{GhezziEtAl2003}.
\end{defn}

@@

The quality of a software's operation is dependent on the degree of correctness
\citep{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable (\citep{GhezziEtAl2003}).

@@

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval (\citep{GhezziEtAl2003}).
\end{defn}

@@

Definition \ref{RobustnessDefnSelected} rephrased:

Software possesses the characteristic of robustness if it fulfills its
requirements correctly or behaves reasonably in circumstances not anticipated in
the requirements specification.

@@

Definition \ref{PerformanceDefnSelected}:

How well or how rapidly the system must perform specific functions. Performance
requirements encompass speed (database response times, for instance), throughput
( transactions per second), capacity (con-current usage loads), and timing (hard
real-time demands).

@@

Combined Definition
\ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}:

The ease with which a software system or component can be modified to correct
faults, improve performance or other attributes, or satisfy new requirements.

@@

Definition \ref{ReusabilityDefnSelected}:

The extent to which a software component can be used with or without adaptation
in a problem solution other than the one for which it was originally developed.

@@

Definition \ref{PortabilityDefnSelected} rephrased:

Effort required to transfer a program between system environments.

>>>>

\begin{defn}
  ``The efficacy of the installation, uninstallation or reinstallation process
  of a software product in a specified environment'' \citep{iso201017043}
\end{defn}

@@

Definition~\ref{DefnInstallability}.  \wss{This definition does not allow for
  measuring the machine time.}

@@

\begin{defn} \label{CorrectDefnSelected} 
  A software is correct if it functions according to its specified functional
  and non-functional specification \citep{GhezziEtAl2003}.  \wss{This is not how
    \citet{GhezziEtAl2003} defines correctness.  They only require satisfaction
    of the functional requirements.}

\end{defn}

@@

The quality of a software's operation is dependent on the degree of correctness
\citep{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable \citep{GhezziEtAl2003}.

@@

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval \citep{GhezziEtAl2003}.
\end{defn}

@@

Definition \ref{RobustnessDefnSelected} rephrased: Software possesses the
characteristic of robustness if it fulfills its requirements correctly or
behaves reasonably in circumstances not anticipated in the requirements
specification. \wss{I think we might want to separate the definition of
  robustness and correctness.  I'm thinking we just want the definition of
  robustness to be how the software behaves in unanticipated circumstances.}

@@

Definition \ref{PerformanceDefnSelected}: How well or how rapidly the system
must perform specific functions. Performance requirements encompass speed
(database response times, for instance), throughput ( transactions per second),
capacity (con-current usage loads), and timing (hard real-time demands).

@@

Combined Definition \ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}: The ease with which a software system or
component can be modified to correct faults, improve performance or other
attributes, or satisfy new requirements.

@@

Definition \ref{ReusabilityDefnSelected}: The extent to which a software
component can be used with or without adaptation in a problem solution other
than the one for which it was originally developed.

@@

Definition \ref{PortabilityDefnSelected} rephrased: Effort required to transfer
a program between system environments.
